Dynamics of isoflurane-induced vasodilation and blood flow of cerebral vasculature revealed by multi-exposure speckle imaging

### 2021-10-26 article.tex
Remove journal name
Response to Reviewer #1

Cranial window implanted mice were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes. The awake hemodynamic baseline was then defined prior to continuous imaging by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}). A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%). Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia. After one minute of exposure ($t = 11$ minutes), the nose-cone was fully positioned over the subject to ensure targeted delivery of isoflurane. After two minutes of exposure ($t = 12$ minutes), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature. The now anesthetized subject was continuously monitored with MESI until $t = 30$ minutes, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames. The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage. Each subject underwent three imaging sessions with at least one full day of recovery between each session.

@@

@@

% ----------------------------------------------------------------------------------------
% BEGIN BIBLIOGRAPHY
% ----------------------------------------------------------------------------------------
\bibliography{bibliography.bib}
\bibliographystyle{elsarticle-num}

>>>>

Cranial window implanted mice were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes. The awake hemodynamic baseline was then defined by acquiring 50 MESI frames, averaging the speckle contrast images across each exposure time, and computing the corresponding MESI $ICT$ image using Eq.~(\ref{eq:mesi}). A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%). Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia. After one minute of exposure ($t = 11$ minutes), the nose-cone was fully positioned over the subject to ensure targeted delivery of isoflurane. After two minutes of exposure ($t = 12$ minutes), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature. The pulse oximeter was also attached and used to monitor vitals and regulate the depth of anesthesia such that the heart rate was matched to within 10\% between imaging sessions for each subject \cite{Kazmi:2013hp}. The now anesthetized subject was continuously monitored with MESI until $t = 30$ minutes, at which point the anesthetized hemodynamic state was defined by acquiring an additional 50 MESI frames. The speckle contrast images were then averaged across each exposure time and used to compute the MESI $ICT$ image using Eq.~(\ref{eq:mesi}). The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage. Each subject underwent three imaging sessions with at least one full day of recovery between each session.

@@

The correction for multiple dynamic scattering events applied to the vascular MESI measurements cannot be directly translated to the parenchyma regions \cite{Kazmi:2015du}. Therefore all parenchyma MESI measurements assume only a single dynamic scattering event per photon, which is not a reliable representation of the underlying dynamics \cite{Davis:2015ij}. Recent efforts to directly measure the intensity autocorrelation function have produced a modified speckle contrast model that assumes both multiple scattering and unordered dynamics \cite{Postnov.2020}. Applying this correction could improve the robustness of the MESI measurements in parenchyma regions, particularly when there are significant reductions in flow.

@@

% ----------------------------------------------------------------------------------------
% BEGIN BIBLIOGRAPHY
% ----------------------------------------------------------------------------------------
\bibliography{bibliography}
\bibliographystyle{elsarticle-num}
